Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach

### 2021-11-28 Documents/Bookdown/10-int-BF.Rmd
update supplemental material

Hypothesis matrices are the same as for the externalizing problems analysis.

@@

Centering and adjusting procedures are the same as for the externalizing problems analysis.

@@

Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-int).

@@

Prior sensitivity analysis is conducted considering the same prior as for the externalizing problems analysis. The results of the prior sensitivity analysis are reported in Table~\@ref(tab:table-sens-prior-analysis-int).

@@

Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data. However, we can observe the same patterns as for the externalizing problems analysis. More diffuse prior, favour hypothesis with more equality constraints. Whereas, tighter prior penalize hypothesis with more equality constraints.

@@

In the model we consider only the role of gender and mother attachment as fixed effects of $\mu$. In the R formula syntax, we have
```{r, echo=TRUE, eval=FALSE}
# formula for p
p ~ gender + (1|ID_class)

@@

To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$ and using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-int).

@@

We can see that the actual variance explained by fixed effects and random effect is around 22\%. Moreover, posterior predictive check indicates a good fit to the data.

>>>>

Hypothesis matrices are the same as in the analysis of the externalizing problems.

@@

Centering and adjusting procedures are the same as in the analysis of the externalizing problems.

@@

Bayes factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-int).

@@

Prior sensitivity analysis is conducted considering the same prior as in the analysis of the externalizing problems. The results of the prior sensitivity analysis are reported in Table~\@ref(tab:table-sens-prior-analysis-int).

@@

Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data. However, we can observe the same patterns as in the analysis of the externalizing problems. More diffuse prior, favour hypothesis with more equality constraints. Whereas, tighter prior penalizes hypotheses with more equality constraints.

@@

In the model, we consider only the role of gender and mother attachment as fixed effects of $\mu$. In the R formula syntax, we have
```{r, echo=TRUE, eval=FALSE}
# formula for p
p ~ gender + (1|ID_class)

@@

To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$ using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-int).

@@

We can see that the actual variance explained by fixed effects and random effects is around 22\%. Moreover, the posterior predictive check indicates a good fit to the data.

### 2021-11-28 Documents/Bookdown/11-int-conclusion.Rmd
update supplemental material

Overall, we obtained consistent results from the three different approaches: only mother attachment influence children's externalizing problems. In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems. Compared to externalizing problems, however, difference between attachment groups are less pronounced. Taken together, these results support the Monotropy Theory.

>>>>

Overall, we obtained consistent results from the three different approaches: only mother attachment influences children's externalizing problems. In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems. Compared to externalizing problems, however, differences between attachment groups are less pronounced. Taken together, these results support the Monotropy Theory.

### 2021-11-28 Documents/Bookdown/index.Rmd
update supplemental material

--- 
title: "Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach"
subtitle: "Supplemental Material"
author: "[Claudio Zandonella Callegher](https://claudiozandonella.netlify.app/), Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["../Biblio-attachment.bib"]
csl: "../apa.csl"
link-citations: yes
github-repo: ClaudioZandonella/Attachment
description: "This the Supplemental Material of the article “Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach”"
cover-image: "images/logo_psicostat.png"
header-includes: 
  - \usepackage{titlepic}
  - \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
url: 'https\://ClaudioZandonella.github.io/Attachment/'
params:
  format: html
---

@@

This is the Supplemental Material of the article “*Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach*” [TODO: add cit]. The aim of the paper is to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.

@@

When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate. Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called “*informative hypotheses*”. However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are unsuitable for testing complex informative hypotheses. An alternative approach is to use the Bayes Factor. In particular, the Bayes Factor based on the “*encompassing prior approach*” allows researchers to easily evaluate complex informative hypotheses. In this paper we provide a clear and detailed introduction to this approach. We describe all the steps and elements involved in the formalization of informative hypotheses and computation of the Bayes Factor following the encompassing prior approach. Subsequently, we provide an application of this method to a real case scenario comparing the different theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development.

@@

In the supplemental material we provide the complete statistical analyses of the case study regarding attachment. For more information regarding the Bayes Factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article]. The supplemental material is structure as follow:

- **Chapter \@ref(case-study) - Case Study.** We describe the sample included in the study and present the results of the cluster analysis to classify the different attachment patterns.
- **Chapter \@ref(ext) - Externalizing Problems.** The analyses regarding externalizing problems are presented. First, we conduct the analysis following the traditional NHST approach. Subsequently, we consider Model Comparison using the AIC and BIC criteria. Finally, we consider the Bayes Factor with encompassing prior approach.
- **Chapter \@ref(int) - Internalizing Problems.** The analyses regarding internalizing problems are presented. The analyses follow the same structure as the case of externalizing problems. Thus, only differences will be highlighted.

>>>>

--- 
title: "Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach"
subtitle: "Supplemental Material"
author: "[Claudio Zandonella Callegher](https://claudiozandonella.netlify.app/), Tatiana Marci, Pietro De Carli, and Gianmarco Altoè"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: ["../Biblio-attachment.bib"]
csl: "../apa.csl"
link-citations: yes
github-repo: ClaudioZandonella/Attachment
description: "This the Supplemental Material of the article “Evaluating informative hypotheses with equality and inequality constraint: A tutorial using the Bayes factor via the encompassing prior approach”"
cover-image: "images/logo_psicostat.png"
header-includes: 
  - \usepackage{titlepic}
  - \titlepic{\includegraphics[width=\textwidth]{images/logo_psicostat.pdf}}
url: 'https\://ClaudioZandonella.github.io/Attachment/'
params:
  format: html
---

@@

This is the Supplemental Material of the article “*Evaluating informative hypotheses with equality and inequality constraints: A tutorial using the Bayes factor via the encompassing prior approach*” [TODO: add cit]. The paper aims to provide a clear and detailed description of the Bayes Factor with the encompassing prior approach considering an applied example.

@@

When conducting a study, researchers usually have expectations based on hypotheses or theoretical perspectives they want to evaluate. Equality and inequality constraints on the model parameters are used to formalize researchers' expectations or theoretical perspectives into the so-called informative hypotheses. However, traditional statistical approaches, such as the Null Hypothesis Significance Testing (NHST) or the model comparison using information criteria (e.g., AIC and BIC), are unsuitable for testing complex informative hypotheses. An alternative approach is to use the Bayes factor. In particular, the Bayes factor based on the encompassing prior approach allows researchers to easily evaluate complex informative hypotheses in a wide range of statistical models (e.g., generalized linear). This paper provides a detailed introduction to the Bayes factor with encompassing prior. First, all steps and elements involved in the formalization of informative hypotheses and the computation of the Bayes factor with encompassing prior are described. Next, we apply this method to a real case scenario, considering the attachment theory. Specifically, we analyzed the relative influence of maternal and paternal attachment on children's social-emotional development by comparing the various theoretical perspectives debated in the literature.

@@

In the supplemental material, we provide the complete statistical analyses of the case study regarding attachment. For more information regarding the Bayes factor with encompassing prior approach or the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article]. The supplemental material is structured into three parts:

#### 1) Presentation {-}

In this section, we describe the aim of the study and the sample included in the study.

- **Chapter \@ref(case-study) - Case Study.** We describe the sample included in the study and present the results of the cluster analysis to classify the different attachment patterns.

#### 2) Externalizing Problems {-}

In this section, we present the analyses evaluating the different roles of mother attachment and father attachment on children's externalizing problems. We follow three different approaches.

- **Chapter \@ref(model-choice-ext) - Models Family Choice.**  We discuss the appropriate models’ family to take into account data characteristics.
- **Chapter \@ref(nhst-ext) - NHST.**  Analysis is conducted following the traditional Null Hypothesis Significance Testing (NHST).
- **Chapter \@ref(model-comparison-ext) - Model Comparison.**  Analysis is conducted according to the  Model Comparison approach using the AIC and BIC criteria.
- **Chapter \@ref(BF-ext) - Bayes Factor.**  Analysis is conducted following the Bayes Factor with the encompassing prior approach.
- **Chapter \@ref(conclusion-ext) - Conclusions.**  Results of the three approaches are discussed.

#### 3) Internalizing Problems {-}

In this section, we present the analyses evaluating the different roles of mother attachment and father attachment on children's internalizing problems. We follow the three different approaches like in the analysis of the externalizing problems. This section is shorter than the previous one as we focus only on the results without repeating all the descriptions of the methods.

- **Chapter \@ref(model-choice-int) - Models Family Choice.**  We discuss the appropriate models’ family to take into account data characteristics.
- **Chapter \@ref(nhst-int) - NHST.**  Analysis is conducted following the traditional Null Hypothesis Significance Testing (NHST).
- **Chapter \@ref(model-comparison-int) - Model Comparison.**  Analysis is conducted according to the  Model Comparison approach using the AIC and BIC criteria.
- **Chapter \@ref(BF-int) - Bayes Factor.**  Analysis is conducted following the Bayes Factor with the encompassing prior approach.
- **Chapter \@ref(conclusion-int) - Conclusions.**  Results of the three approaches are discussed.
